\begin{enumerate}
\item Write the number of zeroes in the end of a number whose prime factorization is $2^2 \times 5^3 \times 3^2 \times 17$.

\item Use Euclid's division algorithm to find the HCF of $255$ and $867$.

\item Find the number of terms in the A.P. :
\begin{align*}
    18,15\frac{1}{2},13, ...,-47.
\end{align*}

\item Determine the A.P. whose third term is $16$ and $7^{th}$ term exceeds the $5^{th}$ term by $12$.

\item Find the value of $x$, when in the A.P. given below
\begin{align*}
2 + 6 + 10 + ... + x = 1800.    
\end{align*}

\item Which term of the A.P. $-4, - 1, 2, ... $is$ 101$?

\item In an A.P., the first term is $- 4$, the last term is $29$ and the sum of all its terms is $150$. Find its common difference.

\item Prove that $2 + 3\sqrt{3}$ is an irrational number when it is given that $\sqrt{3}$ is an irrational number.

\item Prove that $2+5\sqrt{3}$ is an irrational number, given that $\sqrt{3}$ is an irrational number.

\item Using Euclid's Algorithm, find the HCF of $2048$ and $960$.

\item If HCF $\brak{336, 54} = 6$, find LCM $\brak{336, 54}$.

\item Write the smallest number which is divisible by both $306$ and $657$.

\item Find the $21^{st}$ term of the A.P. $-4 \frac{1}{2},-3,-1\frac{1}{2},...$

\item Find the common difference of the Arithmetic Progression (A.P.) 
\begin{align*}
\frac{1}{a} , \frac{3-a}{3a},\frac{3-2a}{3a} , . . (a \neq 0)
\end{align*}

\item Which term of the Arithmetic Progression $-7, -12, -17, -22, ... $ will be $-82$ ? Is $-100$ any term of the A.P. ? Give reason for your answer.

\item How many terms of the Arithmetic Progression $45, 39, 33, ... $must be taken so that their sum is $180$ ? Explain the double answer.

\item Find after how many places of decimal the decimal form of the number $\frac {27}{2^3.5^4.3^2}$ will terminate.

\item Express $429$ as a product of its prime factors.

\item If HCF of $65$ and $117$ is expressible in the form $65n - 117$, then find the value of $n$.

\item On a morning walk, three persons step out together and their steps measure $30 cm$, $36 cm$ and $40 cm$ respectively. What is the minimum distance each should walk so that each can cover the same distance in complete steps ?

\item Prove that $\sqrt{3}$ is an irrational number.

\item Find the largest number which on dividing $1251$, $9377$ and $15628$ leaves remainders $1$, $2$ and $3$ respectively.

\item Find the sum of first $10$ multiples of $6$

\item If $m$ times the $m^{th}$ term of an Arithmetic Progression is equal to $n$ times
its $n^{th}$ term and $m \neq n$, show that the $\brak{m + n}^{th}$ term of the A.P is zero

\item The sum of the first three numbers in an Arithmetic Progression is $18$. If the product of the first and the third term is $5$ times the common
difference, find the three numbers.

\item The HCF of two numbers $a$ and $b$ is $5$ and their LCM is $200 $. Find the product $ab$.

\item Find the HCF of $612$ and $1314$ using prime factorisation.

\item Show that any positive odd integer is of the form $6m + 1$ or $6m + 3$ or $6m + 5$, where $m$ is some integer.

\item Prove that ${\sqrt 5}$ is an irrational number.

\item Prove that $\brak{5 - 3{\sqrt 2}}$ is an irrational number, given that ${\sqrt2}$ is irrational number.

\item Find the sum of all the two digit numbers which leave the remainder $2$ when divided by $5$.

\item If in an A.P ., $a=15$,$d=-3$ and $a_n=0$, then find the value of $n$.

\item If ${S_n}$, the sum of the first ${n}$ terms of an A.P. is given by ${S_n = 2n^2 + n}$,then find its $n^{th}$ term. 

\item If the $17^{th}$ term of an A.P. exceeds its $10^{th}$ term by $7$, find the common difference.

\item If the sum of the first $p$ terms of an A.P. is $q$ and the sum of the first $q$ terms is $p$; then show that the sum of the first $\brak{p + q}$ terms is $\cbrak {-\brak {p + q}}$.

\item Write the common difference of the A.P.${\sqrt3} , {\sqrt12} , {\sqrt27} , {\sqrt48}$ , ... 

\item In an A.P., the $n^{th}$ term is ${\frac{1}{m}}$ and the $m^{th}$ term is $\frac{1}{n}$. Find 
\begin{enumerate}
     \item  $\brak{mn}^{th}$term  ,
     \item sum of first $\brak{mn}$ terms.
\end{enumerate}

\item Find the HCF of $1260$ and $7344$ using Euclid's algorithm.
\item Show that every positive odd integer is of the form $\brak{4q+1}$ or $\brak{4q+3}$, where $q$ is some integer.
\item Which term of the $AP$ $3, 15, 27, 39, ....$ will be $120$ more than its $21$st term?
\item If $S_n$ ,the sum of first $n$ terms of an $AP$ is given by $S_n=3n^2-4n$, find the $n$th term.
\item If the sum of first four terms of an $AP$ is $40$ and that of first $14$ terms is $280$. Find the sum of its first $n$ terms.
\item Prove that $\frac{2+\sqrt{3}}{5}$  is an irrational number, given that $\sqrt{3}$ is an irrational number.
\item The first term of an AP is 3, the last term is 83 and the sum of all its terms is 903. Find the number of terms and the common difference of the AP.
\item Two positive integers $a$ and $b$ can be written as $a = x^3*y^2$ and $b = x*y^3$. x,y are prime numbers. Find $LCM (a, b)$.
\item If the sum of first $n$ terms of an $AP$ is $n^2$, then find its $10$th term.
\end{enumerate}

