\begin{enumerate}
\item Find the intervals in which the function $f\brak{x}=\frac{x^4}{4}-x^{3}-5x^{2}+24x+12 $ is 
\begin{enumerate}
  \item strictly increasing.
 \item strictly decreasing.
\end{enumerate}
 \item Let $A=\{x \in Z : 0 \leq x \leq 12\}$. Show that $R=\{\brak{a,b}: a,b \in A,\mydet{a-b}$ is divisible by $4$\} is equivalence relation.find the set of all elements related to $1$. also write the equivalence class $\brak{2}$.
\item If is defined on the set $\mathbb{R}$ of all real numbers by $ : a * b = \sqrt{a^{2}+b^{2}} ,$ find  the identity element, if it exists in $\mathbb{R}$ with respect to $*$.

\item Let $*$ be a binary operation on $\vec{R} - \cbrak{-1}$ defined by   
$a * b = \frac{a}{b + 1}$for all $a, b \in \vec{R} - \cbrak{-1}$.
show that $*$ is neither commutative nor associative in $\vec{R} - \cbrak{-1}$
commutative nor associative in $\vec{R}-\cbrak{-1}$.
\item If $f\brak{x} = \frac{4x + 3}{6x - 4}$, $x \neq \frac{2}{3}$, Show that $fof\brak{x} = x$ for all $x \neq \frac{2}{3}$. Also, find the inverse of $f$.
\item Find the intervals in which the function $f$ given by $f\brak{x} = 4x^{3}$-6x$^{2}-72x+30$ is
\begin{enumerate}
\item Strictly increasing
\item Strictly decreasing.
\end{enumerate}

\item Show that the relation $S$ in the set $A = \{x \in Z : 0  \le x  \le 12\}$ given by $S= \{\brak{a, b} : a, b \in Z, \vert{a-b}\vert $ is divisible by $ 3 $ \} is an equivalence relation.
\item Let $\ast$ be an operation defined as $\ast : \mathbb{R} \times \mathbb{R} \rightarrow \mathbb{R}$ such that $a\ast b = 2a + b,a, \in \mathbb{R}$.Check if $\ast$ is a binary operation. If yes, find if it is associative too.
\item Let $A$=$R-\cbrak{2}$ and $B$ = $R-\cbrak{1}$. If $f:A \overrightarrow{} B$ is a function defined by $f\brak{x}$=$\dfrac{x-1}{x-2}$, show that $f$ is one-one and onto. Hence, find $f^{-1}$
\item Let $\ast : N \times N \rightarrow N$ be an operation defined as $a \ast b= a+ ab,\forall a,b \in N$. Check if $\ast$ is binary operation. If yes, find if it is associative too.

\item Find the interval in which the function $f$ given by $f\brak{x}=\sin2x+\cos2x,0\leq{x}\leq{\pi}$ is strictly decreasing.

\item  Find whether the function $f\brak{x} = \cos\brak{2x + \dfrac{\pi}{4}}$; is increasing or decreasing in the interval $\dfrac{3\pi}{8} < x < \dfrac{5\pi}{8}$.

\item Prove that the relation $\mathbf{R}$ in the set $A = \cbrak{1,2,3,4,5,6,7}$ given by $\mathbf{R}=\cbrak{a,b}:\mydet{a-b}\text {is even }$ is an equivalence relation.

\item Show that the function $f$ in $A = R-\{\dfrac{2}{3}\}$ defined as $f\brak{x} = \dfrac{4x+3}{6x-4}$ is one-one and onto. Hence, find $f^{-1}$.




