\item DE is drawn parallel to the base $BC$ of a $\triangle ABC$, meeting $AB$ at $D$ and $AC$ at $E$. If $\dfrac{AB}{BD}=4$ and $CE=2$ cm, find $AE$.
\item Prove that the angle between the two tangents drawn from an external point to a circle is supplementary to the angle subtended by the line-segment joining the points of contact at the centre.
\item $S$ and $T$ are points on the sides $PR$ and $QR$ of  $\triangle PQR$ such that $\angle P=\angle RTS$. Show that $\triangle RPQ \sim \triangle RTS$.
\item In an equilateral $\triangle$ ABC, $D$ is a point on the side $BC$ such that $BD=\dfrac{1}{3} BC$. Prove that $9AD^{2}=7AB^{2}$.
\item Prove that the ratio of the areas of two similar triangle is equal to the square of the ratio of their corresponding sides.
\item Prove that in a triangle, if the square of one side is equal to sum of the squares of the other  two sides, the angle opposition the first side is a right angle.
\item A chord of a circle, of radius $15$cm, subtends an angle of $60\degree{}$ at the centre of the circle. Find the area of major and minor segments $\brak{\text{Take }\pi=3.14, \sqrt{3}=1.73}$
\item A sphere of diameter $12$ cm is dropped in a right circular cylindrical vessel, partly filled with water. If the sphere is completely submerged in water, the water level in the vessel rises by $3\dfrac{5}{9}$cm. Find the diameter of the cylindrical vessel.
\item A cylinder whose height is two-third of its diameter, has the same volume as that of a sphere of radius $4$ cm. Find the radius of base of the cylinder.
\item A statue, $1.46$m tall, stands on a pedestal. From a point on the ground the angle of elevation of the top of the statue is $60\degree{}$ and from the same point angle of elevation of the top of the pedestal is $45\degree{}$. Find the height of the pedestal. $\brak{use \sqrt{3}=1.73}$
\end{enumerate}
