\begin{enumerate}
\item The total cost $C\brak{x}$ associated with the production of $x$ units of an item is given by $C\brak{x} = {0.005x}^3-{0.02x}^2+30x+5000$. Find the material cost when $3$ units are produced, where by marginal cost we mean the instantaneous rate of change of total cost at any level of output.

		
\item A black and a red die are rolled together. Find the conditional probability of obtaining the sum $8$, given that the red die resulted in a number less than $4$.
\item Two numbers are selected at random \brak{without\hspace{2pt}replacement} from the first five positive integers. Let $X$ denote the larger of the two numbers obtained. Find the mean and variance of $X$.
\item  Suppose a girl throws a die. If she gets $1$ or $2$, she tosses a coin three times and notes the number of tails. If she gets $3$, $4$, $5$ or $6$, she tosses a coin once and notes whether a 'head' or 'tail' is obtained. If she obtained exactly one 'tail', what is the probability that she threw $3$, $4$, $5$ or $6$ with the die ? 

\item Mother, father and son line up at random for a family photo. If $A$ and $B$ are two events given by $A$ = Son on one end, $B$ = Father in the middle, find $P\brak{\frac{B}{A}}.$
\item Let $X$ be a random variable which assumes values $x_1, x_2, x_3, x_4 $such that 
 \begin{align*}    
   2P\brak{X = x_1} = 3P\brak{X = x_2}= P\brak{X = x_3}= 5P\brak{X = x_4}.
\end{align*}Find the probability distribution of $X$.
 \item A coin is tossed $5$ times. Find the probability of getting $\brak{i}$ at least $4$ heads, and $\brak{ii}$ at most $4 $ heads.
\item There are two boxes $I$ and $II$. Box $I$ contains $3$ red and $6$ black balls. Box $II$ contains $5$ red and $'n'$ black balls. One of the two boxes, box $I$ and box $II$ is selected at random and a ball is drawn at random. The ball drawn is found to be red. If the probability that this red ball comes out from box $II$ is $\frac{3}{5}$, find the value of $'n'$. 

\item Find the mean and variance of the random variable $X$ which denotes the number of doublets in four throws of a pair of dice.

\item The probabilities of solving a specific problem independently by $A$ and $B$ are $\frac{1}{3}$ and $\frac{1}{5}$ respectively. If both try to solve the problem independently, find the probability that the problem is solved.
\item In a multiple choice examination with three possible answers for each of the five questions, what is the probability that a candidate would get four or more correct answers just by guessing ?
\item Out of $8$ outstanding students of a school, in which there are $3$ boys and $5$ girls, a team of $4$ students is to be selected for quiz competition. Find the probability that $2$ boys and $2$ girls are selected .
\item An insurance company insured $3000$ cyclists, $6000$ scooter drivers and $9000$ car drivers. The probability of an accident involving a cyclist, a scooter driver are $0.3$, $0.5$ and $0.02$ respectively. One of the insured person meets with an accident. what is the probability that he is a cyclist ?
\item $12$ cards numbered $1$ to $12$ (one number on one card), are placed in a box and mixed up thoroughly. Then a card is drawn at random from the box. If it is known that number on the drawn card is greater than $5$, find the probability that the card bears an odd number.
\item There are three coins. One is a coin having tails on both faces, another is a biased coin that comes up tail $ 70\% $ of the time and the third is an unbiased coin. One of the coins is chosen at random and tossed, it shows tail. Find the probability that it was a coin with tail on both the faces.
     
\item If $A$ and $B$ are independent events with $P\brak{A}=\frac{3}{7}$ and $P\brak{B}=\frac{2}{5}$, then find $P\brak{A'\bigcap B'}$.

\item If $P\brak{A}=0.6$, $P\brak{B}=0.5$ and $P\brak{B\mid A}=0.4$, find $P\brak{A\cup B}$ and $P\brak{A\mid B}$.
    
\item The probability of two students $A$ and $B$ coming to school on time are $\frac{2}{7}$ and $\frac{4}{7}$, respectively. Assuming that the events '$A$ coming on time' and '$B$ coming on time' are independent, find the probability of only one of them coming to school on time.

\item A bag contains $5$ red and $3$ black balls and another bag contains $2$ red and $6$ black balls. Two balls are drawn at random (without~replacement) from one of the bags and both are found to be red. Find the probability that balls are drawn from the first bag.

\item In answering a question on a multiple choice questions test with four choices in each questions, out of which only one is correct, a student either guesses or copies or knows the answer. The probability that he makes a guess is $\frac{1}{4}$ and the probability the he copies is also $\frac{1}{4}$. The probability that the answer is correct, given that he copied it is $\frac{3}{4}$. Find the probability that he knows the answer to the question, given that  he correctly answered it.

\item A card from a pack of $52$ playing cards is lost. From the remaining cards of the pack, two cards are drawn at random (without~replacement) and both are found to be spades. Find the probability of the lost card being a spade.

\item Four cards are drawn one by one with replacement from a well-shuffled deck of playing cards. Find the probability that at least three cards are of diamonds.



