\begin{enumerate}
	\item Find the magnitude of each of the vectors $\overrightarrow{\mathbf{a}}$ and $\overrightarrow{\mathbf{b}}$, having the same magnitude such that the angle between them is ${60\degree}$ and their scalar product is $\frac{9}{2}$.
 
 \item Find the shortest distance between the lines $\overrightarrow{\mathbf{r}}=\brak{4\hat{i}-\hat{j}}+\lambda\brak{\hat{i}+2\hat{j}-3\hat{k}}$ and $\overrightarrow{\mathbf{r}}=\brak{\hat{i}-\hat{j}+2\hat{k}}+\mu\brak{2\hat{i}+4\hat{j}-5\hat{k}-} $.

\item Show that the function $f:\mathbb{R}\rightarrow \mathbb{R}$ defined by $f\brak{x} = \frac{x}{x^{2}+1}, \forall \mathbf{x}\in \mathbb{R}$ is neither one-one nor onto. Also, if $g:\mathbb{R} \rightarrow \mathbb{R}$ is defined as $g\brak{x}=2x-1$, find $fog\brak{x}$.

\item If $\theta$ is the angle between the two vectors $\hat{i}-2\hat{j}+3\hat{k}$ and $3\hat{i}-2\hat{j}+\hat{k}$, find $\sin\theta$.

\item  Find the distance of the point \brak{-1,-5,-10} from the point of intersection of the line $\overrightarrow{\mathbf{r}}=2\hat{i}-\hat{j}+2\hat{k} + \lambda\brak{3\hat{i}+4\hat{j}+2\hat{k}}$ and the plane $\overrightarrow{\mathbf{r}}\cdot\brak{\hat{i}-\hat{j}+\hat{k}}=5$.

\item Let $\overrightarrow{\mathbf{a}}=4\hat{1}+5\hat{j}-\hat{k}$,$\overrightarrow{\mathbf{b}}=\hat{i}-4\hat{j}+5\hat{k}$ and $\overrightarrow{\mathbf{c}}=3\hat{i}+\hat{j}-\hat{k}$. find a vector $\overrightarrow{\mathbf{d}}$ which is perpendicular to both $\overrightarrow{\mathbf{c}}$ and $\overrightarrow{\mathbf{b}}$ and $\overrightarrow{\mathbf{d}}\cdot \overrightarrow{\mathbf{a}}=21$

\item If a line has the direction ratios $-18, 12, -4,$ then what are its direction cosines ?
\item Find the cartesian equation of the line which passes through the point $\brak{-2, 4, -5}$ and is parallel to the line $\frac{x+3}{3}=\frac{4-y}{5}=\frac{z+8}{6}$.
\item Find a unit vector perpendicular to both the vectors $\overrightarrow{a}$ and $\overrightarrow{b}$ , where $\overrightarrow{a} = \hat{i} -7 \hat{j} + 7\hat{k}$ and $\overrightarrow{b} = 3\hat{i} -2 \hat{j} + 2\hat{k}$ .

\item Show that the vectors $\hat{i} -2 \hat{j} + 3\hat{k}$, $2\hat{i} +3 \hat{j} -4\hat{k}$ and $\hat{i} -3 \hat{j} + 5\hat{k}$ are coplanar.
 \item Let $\overrightarrow{a}$, $\overrightarrow{b} $ and $\overrightarrow{c}$ be three vectors such that $\abs{\overrightarrow{a}}=1$, $\abs {\overrightarrow{b}}=2 $ and $\abs{\overrightarrow{c}}=3$. If the projection of $\overrightarrow{b}$ along $\overrightarrow{a}$ is equal to the projection of $\overrightarrow{c}$ along $\overrightarrow{a}$ ; and $\overrightarrow{b}$, $\overrightarrow{c}$ are perpendicular to each other, then find $\abs{3\overrightarrow{a}- 2\overrightarrow{b} +2\overrightarrow{c}}$.

\item Find the vector and cartesian equations of the plain passing through the points $\brak{2,5,-3},\brak{-2,-3,5}$ and $\brak{5,3,-3}$. also find the point of intersection of this plane with the line passing through points $\brak{3,1,5}$ and $\brak{-1,-3,-1}$.

\item Find the equation of the plane passing through the intersection of the planes $\overrightarrow{r} \cdot\brak{\hat{i} + \hat{j} + \hat{k}}=1$ and $\overrightarrow{r} \cdot \brak{ 2\hat{i}+3\hat{j}-\hat{k}} +4=0$ and parallel to $x-axis$. Hence, find the distance of plane from $x-axis$.

\item Find the direction cosines of the line joining points $P$ $\brak{4,3,-5}$ and $Q$ $\brak{-2,1,8}$.

\item Find the value of $P$ for which the following lines are perpendicular:
 \begin{align*}
 \frac{1-x}{3}=\frac{2y-14}{2p}=\frac{z-3}{2}; \frac{1-x}{3p}=\frac{y-5}{1}=\frac{6-z}{5}
 \end{align*}
 \item Find the value of $\lambda$ for which the following lines are perpendicular to each other:
 \begin{align*}
 \dfrac{x-5}{5\lambda+2}= \dfrac{2-y}{5} = \dfrac{1-z}{-1};\dfrac{x}{1}=\dfrac{y+\dfrac{1}{2}}{2\lambda}=\dfrac{z-1}{3} 
 \end{align*}
Hence, find whether the lines insert or not.

\item Fnd the value of $x$ such that the four points with position vectors,
$\mathbf{A}\brak{3\hat{i} + 2\hat{j} + \hat{k}}$, $\mathbf{B}\brak{4\hat{i} + x\hat{j} + 5\hat{k}}$, $\mathbf{C}\brak{4\hat{i} + 2\hat{j} -2 \hat{k}}$, $\mathbf{D}\brak{6\hat{i} + 5\hat{j} - \hat{k}}$ are coplanar.
\item Find the vector equation of the plane which contains the line of intersection of the planes $ \overrightarrow{r}.\brak{\hat{i} + 2\hat{j}+3\hat{k}}-4=0$ , $\overrightarrow{r}.\brak{2\hat{i} + \hat{j} - \hat{k}}+5=0$ and which is perpendicular to the plane $\overrightarrow{r}.\brak{5\hat{i} + 3\hat{j} - 6\hat{k}}+8=0$.
\item Find the value of $x$, for which the four points $\mathbf{A}\brak{x,1,-1}$, $\mathbf{B}\brak{4,5,1}$, $\mathbf{C}\brak{3,9,4}$ and $\mathbf{D}\brak{-4,4,4}$ are coplanar.
\item Find the acute angle between the planes $\vec{r}$($ \hat{i}-\hat{2j}-\hat{2k})=1$ and $\vec{r}$($ \hat{3i}-\hat{6j}+\hat{2k})=0$
\item Let $\vec{a}=\hat{i}+\hat{2j}-\hat{3k}$ and $\vec{b}=\hat{3i}-\hat{j}+\hat{2k}$ be two vectors. Show that the vectors $(\vec{a}+\vec{b})$ and $(\vec{a}-\vec{b})$ are perpendicular to each other.
\item Find the coordinates of the foot of the perpendicular $\mathbf{Q}$ drawn from $\mathbf{P}(3, 2, 1)$ to the plane $2x - y + z + 1 = 0$. Also, find distance $\mathbf{PQ}$ and the image of the point $\mathbf{P}$ treating this plane as a mirror.
\item Find the vector equation of the plane determined by the points $\mathbf{A}\brak{3,-1,2}$, $\mathbf{B}\brak{5,2,4}$, $\mathbf{C}\brak{-1,-1,6}$. Hence, find the distance of the plane, thus obtained, from the origin.
\item $\mathbf{X}$ and $\mathbf{Y}$ are two points with position vectors $3\overrightarrow{a}+\overrightarrow{b}$ and$\overrightarrow{a}-3\overrightarrow{b}$ respectively. Write the position vector of a point $\mathbf{V}$ which divides the line segment $\mathbf{XY}$ in the ratio $2:1$ externally.
\item Find the vector equation of a line passing through the point $(2,3,2)$ and parallel to the line $\overrightarrow{r} = \brak{-2\hat{i}+3\hat{j}}+\lambda\brak{2\hat{i}-3\hat{j}+6\hat{k}}$. Also, find the distance these two lines.
\item  Find the vector equation of the line passing through $\brak{2, 1, -1}$ and parallel to the line $\overrightarrow{r}=\brak{\hat{i}+\hat{j}}+\lambda\brak{2\hat{i}-\hat{j}+\hat{k}}$. Also, find the distance between these two lines.

\item For any two vectors $\overrightarrow{a}$ and $\overrightarrow{b}$, prove that
    \begin{align*}
    \brak{{\overrightarrow{a} \times \overrightarrow{b}}}^{2} = {\overrightarrow{a}^{2}}~~{\overrightarrow{b}^{2}} - \brak{{\overrightarrow{a} \cdot \overrightarrow{b}}}^{2} 
    \end{align*}

\item Find the equation of planes passing through the intersection  of the planes $\overrightarrow{r} \cdot \brak{2\hat{i}+6\hat{j}}+12=0$ and $\overrightarrow{r} \cdot \brak{3\hat{i}-\hat{j}+4\hat{k}}=0$ and are at a unit distance from origin.

\item Using vectors, find the value of $x$ such that the four points $\mathbf{A}$ $\brak{x,5,-1}$,$\mathbf{B}$ $\brak{3,2,1}$,$\mathbf{C}$ $\brak{4,5,5}$ and $\mathbf{D}$ $\brak{4,2,-2}$ are coplanar.

\item Find the angle between the line $\overrightarrow{r}=\brak{2\hat{i}-\hat{j}+3\hat{k}}+\lambda\brak{3\hat{i}-\hat{j}+2\hat{k}}$ and the plane $\overrightarrow{r}.\brak{\hat{i}+\hat{j}+\hat{k}}=3$.

\item Using vectors, prove that the points $\brak{2,-1,3},\brak{3,-5,1}$ and $\brak{-1,11,9}$ are collinear.




