\begin{enumerate}
\item Obtain all the zeroes of the polynomial $2x^4 - 5x^3 - 11x^2 + 20x + 12$ when $ 2 $ and $ -2 $ are two zeroes of the above polynomial. 

\item Find the quadratic polynomial, sum and product of whose zeroes are $-1$ and $-20$ respectively. Also find the zeroes of the polynomial so obtained.

\item Sum of the areas of two squares is $157 m^2$. If the sum of their perimeters is $68 m$, find the sides of the two squares.

\item A plane left $30$ minutes later than the scheduled time and in order to reach its destination $1500 km$ away on time, it has to increase its speed by $250 km/hr$ from its usual speed. Find the usual speed of the plane.

\item A motorboat whose speed is $18$ km/hr in still water takes one hour more to go $24 km$ upstream than to return downstream to the same spot. Find the speed of the stream.

\item Solve for $x$ :
\begin{align*}
    \frac{1}{2a+ b +2x} = \frac{1}{2a}+\frac{1}{b}+\frac{1}{2x}; x\neq0, x\neq\frac{-2a-b}{2}, a, b\neq0
\end{align*}

\item The sum of the areas of two squares is $640 m^2$. If the difference of their perimeters is $64m$, find the sides of the square.

\item For what values of $k$ does the quadratic equation $4x^2 - 12x - k = 0$ have 
no real roots ?
\item  Evaluate:
\begin{align*}
    \frac {\tan 65\degree}  {\cot 25\degree}
\end{align*}

\item Express $\brak{{\sin 67\degree}+ {\cos 75\degree}}$ in terms of trigonometric ratios of the angle between $0\degree$ and $45\degree$.

\item Prove that :
\begin{align*}
    \brak{\sin \theta+1+\cos \theta} \brak{\sin\theta-1+\cos\theta}.\sec\theta \csc\theta=2
\end{align*}

\item Prove that :
\begin{align*}
      \sqrt{\frac{\sec\theta-1}{\sec\theta+1}} + \sqrt{\frac{\sec\theta+1}{\sec\theta-1}} = 2\csc\theta
\end{align*}

\item If $\sec\theta + \tan\theta=m$, show that $\frac{m^2-1}{m^2+1} = \sin\theta$.

\item Prove that :
\begin{align*}
    2 (\sin^6\theta +\cos^6\theta) - 3 (\sin^4\theta + \cos^4\theta) + 1 = 0
\end{align*}

\item Find $A$ and $B$ if $\sin \brak{A + 2B}=\frac{\sqrt{3}}{2}$ and $\cos \brak{A + 4B} = 0$, where $A$ and $B$ are acute angles.

\item For what value of $k$, is the polynomial $f\brak{x} = 3x^4-9x^3+x^2+15x+k$ completely divisible by $3x^2 - 5$ ?

\item The total cost of a certain length of a piece of cloth is {\rupee$200$}. If the piece was $5 m$ longer and each metre of cloth costs {\rupee $2$ less}, the cost of the piece would have remained unchanged. How long is the piece and what is its original rate per metre ?

\item In a class test, the sum of Arun's marks in Hindi and English is $0$. Had he got $2$ marks more in Hindi and $3$ marks less in English, the product of the marks would have been $210$. Find his marks in the two subjects. 

\item Find the nature of the roots of the quadratic equation 
 \begin{align*}
 4x^2 + 4\sqrt{3}x +3= 0 
 \end{align*}

 \item Write all the values of $p$ for which the quadratic equation $x^2 + px + 16 = 0$ has equal roots. Find the roots of the equation so obtained.

\item Find the zeroes of the quadratic polynomial $7y^2 -\frac{11}{3}y -\frac{2}{3}$ and verify the relationship between the zeroes and the coefficients.

\item Solve for $x$ :
\begin{align*}
x^2+5x-\brak{a^2 +a -6}=0
\end{align*}

\item Find the nature of roots of the quadratic equation $2x^2-4x-3=0$.

\item Evaluate :
 \begin{align*}
	     \sin^{2}{60\degree} + 2\tan{45\degree} - \cos^{2}{30\degree}. 
      \end{align*}

\item Evaluate :
\begin{align*}
\left(\frac{3\tan 41\degree}{\cot 90\degree}\right)^2 - \left(\frac{\sin 3\degree \sec 55\degree}{\tan 10\degree \tan 20\degree \tan 60\degree \tan 70\degree \tan 80\degree}\right)^2
\end{align*}

\item Prove that :
\begin{align*}
\frac{\tan \theta}{1-\cot \theta} + \frac{\cot \theta}{1- \tan \theta} = 1+ \sec \theta  \csc  \theta   
\end{align*}

\item Prove that :
\begin{align*}
    \frac{\sin \theta}{\cot \theta + \csc \theta} = 2 + \frac{\sin \theta}{\cot \theta - \csc \theta}
\end{align*}

\item Evaluate :
\begin{align*}
\left(\frac{3\sin 43\degree}{\cos 47\degree}\right)^2 - \frac{\cos 37\degree \csc 53\degree}{\tan 5\degree \tan 25\degree \tan 45\degree \tan 65\degree \tan 85\degree}
\end{align*}

\item The larger of two supplementary angles exceeds the smaller by $18\degree$. Find the angles.

 \item If $\sin A = \frac{3}{4}$, calculate $\sec A$.

\item Write the discriminant of the quadratic equation $\brak {x + 5}^2 = 2 \brak {5x {-3}}$.

\item Using completing the square method, show that the equation
$x^2 - 8x + 18 = 0$ has no solution.

\item Check whether $g\brak{x}$ is a factor of $p\brak{x}$ by dividing polynomial $p\brak{x}$ by polynomial $g\brak{x}$,where $p\brak{x} = x^5 - 4x^3 + x^2 + 3x + 1$ , $g\brak{x} = x^3 - 3x + 1$

\item If $\frac{2}{3}$ and $-3$ are the zeroes of the polynomial $ax^2 + 7x + b$, then find the values of $a$ and $b$.

\item If $\tan$ $\alpha$ = ${\frac {5}{12}}$, find the value of $\sec$ $\alpha$.

\item $A$, $B$ and $C$ are interior angles of a triangle $ABC$. Show that
\begin{enumerate}
\item  $\sin$ $ \brak{{\frac {B+C}{2}}} = \cos {\frac {A}{2}}$
\item  If $\angle A = 90 \degree$ , then find the value of $\tan \brak{{\frac{B+C}{2}}}$ 
\end{enumerate} 

\item If $\tan \brak{A + B} = 1$ and $\tan \brak{A - B} = \frac{1}{\sqrt{3}}$ , $0\degree$ $<$ $A + B$ $<$ $90\degree$, $A > B$, then find the values of $A$ and $B$.

\item If $1 + \sin^2 \theta  = 3 \sin \theta \cos \theta$, then prove that $\tan$ $\theta = 1 $ or $\tan$ $\theta = \frac{1}{2}$

\item Prove that :
\begin{align*}
\frac{\tan^3 \theta}{1+\tan^2 \theta} + \frac{\cot^3 \theta}{1 + \cot^2 \theta} =  \sec \theta  \csc  \theta - 2 \sin \theta \cos \theta  
\end{align*}

\item A motorboat whose speed in still water is $9 km/h $, goes $15km$ downstream and comes back to the same spot, in a total time of $3 hours$ $45 minutes$. Find the speed of the stream.


\item Find all the zeroes of the polynomial $x^4 + x^3- 14x^2 -2x + 24$, if two of its zeroes are $\sqrt2$ and $-\sqrt 2$ .

\item Apply division algorithm to check if $g\brak{x} = x^2 - 3x + 2$ is a factor of the polynomial $f\brak{x} = x^4 - 2x^3 - x + 2$.


\item A train travels $360 km$ at a uniform speed. If the speed had been $5 km/hr$ more, it would have taken $1 hr$ less for the same journey. Find the speed of the train.

\item Find the value of $k$ for which $x = 2$ is a solution of the equation
  $kx^2 + 2x - 3 = 0$.
  
\item Find the value/s of $k$ for which the quadratic equation $3x^{2} + kx + 3 = 0$
has real and equal roots.


\item Solve for $x$ :
\begin{align*}
    {\frac {1}{a+b+x}} = {\frac{1}{a}} + {\frac{1}{b}} + {\frac{1}{x}};  {a\neq b \neq 0},{x \neq 0},{x \neq -(a+b)}
\end{align*}

\item If $\sin{x} + \cos{y}= 1$ ; $x=30\degree$  and  $y$ is an acute angle, find the value of $y$ .

\item Find the value of $\cos {48\degree} - \sin {42\degree}$.

\item Prove that :
\begin{align*}
   {\frac{\tan\theta}{1-\tan\theta}} - {\frac{\cot\theta}{1-\cot\theta}}={\frac{\cos\theta+ \sin\theta}{\cos\theta-\sin\theta}}
\end{align*} 

\item If ${\cos\theta + \sin\theta} = {\sqrt 2}{\cos\theta}$, show that ${\cos\theta - \sin\theta} = {\sqrt 2}{\sin\theta}$.

\item Prove that :
\begin{align*}
    {\frac{(1+\cot\theta+\tan\theta)(\sin\theta-\cos\theta)}{(\sec^3\theta-\csc^3\theta)}} = \sin^2\theta \cos^2\theta
\end{align*}

\item Evaluate :
\begin{align*}
    {\frac{\csc^2(90\degree - \theta)-\tan^2\theta)}{2(\cos^2 37\degree + \cos^2 53\degree)}} - {\frac{2\tan^2 30\degree \sec^2 37\degree \cdot \sin^2 53\degree}{\csc^2 63\degree - \tan^2 27\degree}} 
\end{align*}	




\item For what values of $k$, the roots of the equation $x^2+4x+k = 0$ are real?
  \item Find the value of $k$ for which the roots of the equation $3x^2-10x+k=0$ are reciprocal of each other.
  \item How many two digits numbers are divisible by $3$ ?
  \item Find a rational number between $\sqrt{2}$ and $\sqrt{3}$.
  
  \item Find $c$ if the system of equations $cx+3y+(3-c)=0$; $12x+cy-c=0$ has infinitely many solutions.
  \item Find the value of $k$ such that the polynomial $x^2-\brak{k+6}x+2\brak{2k-1}$ has sum of its zeros equal to half of their product.
  \item Two water taps together can fill a tank in $1\frac{7}{8}$ hours. The tap with longer $8$ diameter takes $2$ hours less than the tap with smaller one to fill the tank separately. Find the time in which each tap can fill the tank separately.
  
  
  
  
  \item Prove that $\sqrt{2}$ is an irrational number.
  \item Prove that \begin{align*} \brak{\sin\theta + \csc\theta}^2 + \brak{\cos\theta + \sec\theta}^2 = 7 + \tan^2\theta + \cot^2\theta\end{align*}.
  \item Prove that \begin{align*}\brak{1+\cot A - \csc A} \brak{1 + \tan A +\sec A} = 2 \end{align*}.
  \item Prove that \begin{align*} \frac{\sin A-\cos A+1}{\sin A+ \cos A-1} =\frac{1}{\sec A-\tan A}\end{align*}
  \item Find $A$ if \begin{align*}\tan 2A = \cot (A-24\degree)\end{align*}
  \item Find the value of \begin{align*}(\sin^2 33\degree+ \sin^2 57\degree)\end{align*}
  
  
  \item Find all zeros of the polynomial $3x ^ 3 + 10x ^ 2 - 9x - 4$ if one of its zero is $1$.
   
  \item if If $\sec\theta = x + \frac{1}{4x}$, where $x \neq 0$, find $(\sec\theta + \tan\theta)$.
  \item prove that \begin{align*} \frac{\tan^2A}{\tan^2 A-1}+\frac{\csc^2 A}{\sec^2 A-\csc^2 A}=\frac{1}{1-2\cos^2 A}\end{align*}
  \end{enumerate}
