\begin{enumerate}
\item Find the solution of the pair of equations :
\begin{align*}
    \frac{3}{x}+\frac{8}{y}=-1; \frac{1}{x}-\frac{2}{y}=2, x, y\neq 0
\end{align*}

\item Find the value(s) of $k$ for which the pair of equations
\begin{align*}
    kx+2y=3\\
3x+6y=10
\end{align*}
has a unique solution.
\item Sumit is $3$ times as old as his son. Five years later, he shall be two and a half times as old as his son. How old is Sumit at present ?

 \item Find the value(s) of $k$ so that the pair of equations $x + 2y = 5$ and $3x + ky + 15 = 0$ has a unique solution.

 \item For what value of $k$, will the following pair of equations have infinitely many solutions :
\begin{align*}
	2x + 3y = 7 \hspace{2pt} \text{and} \hspace{2pt} \brak{k+2}x - 3\brak{1-k}y = 5k+1 
\end{align*}

\item Solve the following pair of linear equations :
\begin{align*}
 3x - 5y = 4\\
2y + 7 = 9x   
\end{align*}    

\item Solve the following pair of linear equations :
\begin{align*}
 3x + 4y = 10\\
2x - 2y = 2   
\end{align*}    

\item Find the value of $k$ so that the area of triangle $ABC$ with $A\brak{k + 1, 1}$, $B\brak{4, -3}$ and $C\brak{7, -k}$ is $6$ square units.


\item For what value of $k$, does the system of linear equations\\
\begin{align*}
   2x + 3y = 7\\
 \brak{k - 1} x + \brak{k + 2} y = 3k
\end{align*}
have an infinite number of solutions ?

\item A part of monthly hostel charges in a college hostel are fixed and the remaining depends on the number of days one has taken food in the mess. When a student $A$ takes food for $25$ days, he has to pay {\rupee $4,500$}, whereas a student $B$ who takes food for $30$ days, has to pay {\rupee $5,200$}. Find the fixed charges per month and the cost of food per day.


\item A father's age is three times the sum of the ages of his two children. After $5$ years his age will be two times the sum of their ages. Find the present age of the father.
\item A boat goes $30 \,\text{km}$ upstream and $44 \,\text{km}$ downstream in $10$ hours. In $13$ hours, it can go $40\,\text{km}$ upstream and $55 \,\text{km}$ downstream. Determine the speed of the stream and that of the boat in still water.

\item A fraction becomes $\frac{1}{3}$ when $2$ is subtracted from the numerator and it becomes $\frac{1}{2}$ when $1$ is subtracted from the denominator.Find the fraction.

\item Find the value of $k$ for which the following pair of linear equations have infinitely many solutions. $2x+3y=7$ , $(k+1)x+(2k-1)y=4k+1$
\end{enumerate}

