\begin{enumerate}
\item A company produces two types of goods, $A$ and $B$, that require gold and silver. Each unit of type $A$ requires $3$ g of silver and $1$ g of gold while that of type $B$ requires $1$ g of silver and $2$ g of gold. The company can use at the most $9$ g of silver and $8$ g of gold. If each unit of type $A$ brings a profit of \rupee $40$ and that of type $B$ \rupee $50$, find the number of units of each type that the company should produce to maximize profit. Formulate the above LPP and solve it graphically and also find the maximum profit.

\item Show that the height of the cylinder of maximum volume that can be inscribed in a sphere of radius $R$ is $\frac{2R}{\sqrt{3}}$. Also find the maximum volume.

\item The volume of a cube is increasing at the rate of $8 cm^3/s$. How fast is the surface area increasing when the length of its edge is $12 cm$ ?

\item A dietician wishes to mix two types of food in such a way that the vitamin contents of the mixture contains at least $8$ units of vitamin $A$ and $10$ units of vitamin $C $. Food $I $ contains $2$ units/kg of vitamin $A$ and $1$ unit/kg of vitamin $C$. It costs \rupee$50$ per kg to produce food $I$. Food $II$ contains $1$ unit/kg of vitamin $A$ and $2$ units/kg of vitamin $C$ and it costs \rupee $70$ per kg to produce food $II$. Formulate this problem as a LPP to minimise the cost of a mixture that will produce the required diet. Also find the minimum cost.


\item A manufacturer produces nuts and bolts. It takes $1$ hour of work on machine $A$ and $3$ hours on machine $B$ to produce a package of nuts. It takes $3$ hours on machine $A$ and $1$ hour on machine $B$ to produce a package of bolts. He earns a profit of \rupee~35 per package of nuts and \rupee~14 per package of bolts. How many packages of each should be produced each day so as to maximise his profit, if he operates each machine for atmost $12$ hours a day ? Convert it into an LPP and solve graphically.

