\begin{enumerate}
\item If $P(not A) =0.7$, $P(B)=0.7$ and $P(B\mid A)=0.5$, then find $P(A\mid B)$.

\item A coin is tossed $5$ times. What is the probability of getting 
\begin{enumerate}[label=(\roman*)]
    \item $3$ heads
    \item at most $3$ heads
\end{enumerate}

\item Find the probability distribution of $X$, the number of heads in a simultaneous toss of two coins.

\item There are three coins. One is a two-headed coin, another is a biased coin that comes up heads $75\%$ of the time and the third is an unbiased coin. One of the three coins is chosen at random and tossed. If it shows heads, what is the probability that it is the two-headed coin ?

\item A bag contains $5$ red and $4$ black balls, a second bag contains $3$ red and $6$ black balls. One of the two bags is selected at random and two balls are drawn at random (without replacement) both of which are found to be red. Find the probability that the balls are drawn from the second bag.

\item In a multiple choice examination with three possible answers for each of the five questions, what is the probability that a candidate would get four or more correct answers just by guessing ?

\item The probabilities of solving a specific problem independently by $A$ and $B$ are $\frac{1}{3}$ and $\frac{1}{5}$ respectively. If both try to solve the problem independently, find the probability that the problem is solved.

\item There are three coins. One is a coin having tails on both faces, another is a biased coin that comes up tails $70\%$ of the time and the third is an unbiased coin. One of the coins is chosen at random and tossed, it shows tail. Find the probability that it was a coin with tail on both the faces.


