\begin{enumerate}
\item A bag contains $15$ balls, out of which some are white and the others are black. If the probability of drawing a black ball at random from the bag is $\frac{2}{3}$, then find how many white balls are there in the bag.

\item A card is drawn at random from a pack of $52$ playing cards. Find the probability of drawing a card which is neither a spade nor a king.

\item A die is thrown once. Find the probability of getting
\begin{enumerate}
    \item a prime number
    \item an odd number. 
\end{enumerate}

\item Three different coins are tossed simultaneously. Find the probability of getting exactly one head.

\item A die is thrown twice. Find the probability that
\begin{enumerate}
\begin{item}
  $5$ will come up at least once .
 \item $5$ will not come up either time .
\end{item}
\end{enumerate}

\item The probability of selecting a blue marble at random from a jar that contains only blue, black and green marbles is $\frac{1}{5}$. The probability of selecting a black marble at random from the same jar is $\frac{1}{4}$. If the jar contains $11$ green marbles, find the total number of marbles in the jar.

\item A die is thrown once. Find the probability of getting
\begin{enumerate}
\item a composite number,
\item a prime number.
\end{enumerate}

\item Cards numbered $7$ to $40$ were put in a box. Poonam selects a card at
random. What is the probability that Poonam selects a card which is a
multiple of $7$ ?

\item A child has a die whose $6$ faces show the letters given below :
\begin{align*}
    { \framebox {A} \hspace{1cm}} {\framebox {B} \hspace{1cm}} {\framebox {C}\hspace{1cm}} {\framebox {A}\hspace{1cm}} {\framebox {A}\hspace{1cm}} {\framebox {B}}
\end{align*}

\item Cards marked with numbers $5$ to $50$ (one number on one card) are placed in a box and mixed thoroughly. One card is drawn at random from the box. Find the probability that the number on the card taken out is \begin{enumerate}
    \item a prime number less than $10$,  
    \item a number which is a perfect square.
\end{enumerate}

\item Find the probability that a number selected at random from the numbers $3, 4, 4, 4, 5, 5, 6, 6, 6, 7$ will be their mean.
	\item A game consists of tossing a coin $3$ times and noting the outcome each time. If getting the same result in all the tosses is a success, find the probability of losing the game.
	\item A die is thrown once. Find the probability of getting a number.
	\begin{enumerate}
	\item which is a prime number
	\item lies between $2$ and $6$.
	\end{enumerate}

\end{enumerate}
