 \begin{enumerate}
 \item A line passes through the point with position vector $2\hat{i}-\hat{j}+4\hat{k}$ and is in the direction of the vector $\hat{i}+\hat{j}-2\hat{k}$. Find the equation of the line in cartesian form.
 
\item If ${\overrightarrow{\mydet{a}}}$ = $2, {\overrightarrow{\mydet{b}}}$ = $7$ and $\overrightarrow{a}\times\overrightarrow{b}$ = $3\hat{i}+2\hat{j}+6\hat{k}$, find the angle between $\overrightarrow{a}$ and $\overrightarrow{b}$.

\item Find the volume of a cuboid whose edges are given by $-3\hat{i}+7\hat{j}+5\hat{k}$,$-5\hat{i}+7\hat{j}-3\hat{k}$ and $7\hat{i}-5\hat{j}-3\hat{k}$.


\item The scalar product of the vector $\overrightarrow{a} = \hat{i}+\hat{j}+\hat{k}$ with a unit vector along the sum of the vectors $\overrightarrow{b} = 2\hat{i}+4\hat{j}-5\hat{k}$ and $\overrightarrow{c} = \hat{\lambda}+2\hat{j}+3\hat{k}$ is equal to $1$. Find the value of $\lambda$ and hence find the unit vector along $\overrightarrow{b}+\overrightarrow{c}$.

\item Find the vector and cartesian equations of the plane passing through the points having position vectors $\hat{i}+\hat{j}-2\hat{k}$, $2\hat{i}-\hat{j}+\hat{k}$ and $\hat{i}+2\hat{j}+\hat{k}$. Write the equation of a plane passing through a point \myvec{2, 3, 7} and parallel to the plane obtained above. Hence, find the distance between the two parallel planes.

\item Find the cartesian and vector equations of the plane passing through the points $A$\brak{2,5,-3}, $B$\brak{-2,-3,5} and $C$\brak{5,3,-3}.

 \item Show that the points $A\brak{-2\hat{i}+3\hat{j}+5\hat{k}}$, $B\brak{\hat{i}+2\hat{j}+3\hat{k}}$ and $C\brak{7\hat{i}-\hat{k}}$ are collinear.
 
 \item Find $\mydet{\overrightarrow{a}\times\overrightarrow{b}}$, if $\overrightarrow{a}=2\hat{i}+\hat{j}+3\hat{k}$ and $\overrightarrow{b}=3\hat{i}+5\hat{j}-2\hat{k}$.
 
 \item Using integration, find the area of the triangular region whose sides have the equations ${y}={2x}+1$, ${y}={3x}+1$ and ${x}=4$.

 \item Using method of integration, find the area of the triangle whose vertices are $\myvec{1,0}$,$\myvec{2,2}$ and $\myvec{3,1}$.
 
 \item Find the direction cosines of a line which makes equal angles with the coordinate axes.
         
 \item If the lines $\frac{x-1}{-3}=\frac{y-2}{2\lambda}=\frac{z-3}{2}$ and $\frac{x-1}{3\lambda}=\frac{y-1}{2}=\frac{z-6}{-5}$ are perpendicular, find the value of $\lambda$. Hence find weather the lines are intersecting or not.
           
\item Find the equation of the line passing through \brak{2, – 1, 2} and \brak{5, 3, 4} and of the plane passing through \brak{2, 0, 3}, \brak{1, 1, 5} and \brak{3, 2, 4}. Also, find their point of intersection.
\item Find the vector equation of the plane which contains the line of intersection of the planes 
$ \overrightarrow{r}.\brak{\hat{i} + 2\hat{j}+3\hat{k}}-4=0$ , $\overrightarrow{r}.
\brak{2\hat{i} + \hat{j} - \hat{k}}+5=0$ and which is perpendicular to the plane $\overrightarrow{r}.\brak{5\hat{i} + 3\hat{j} - 6\hat{k}}+8=0$.

\item Find the vector equation of a line passing through the point
$\brak{2, 3, 2}$ and parallel to the line $\overrightarrow{r}=\brak{-2\hat{i} +3\hat{j}}\lambda\brak{2\hat{i} - 3\hat{j}+6\hat{k}}$.
Also, find the distance between these two lines.

\item Find the value of $\vec{x}$ such that the four points with position vectors,
$\vec{A}\brak{3\hat{i} + 2\hat{j} + \hat{k}}$, $\vec{B}\brak{4\hat{i} + x\hat{j} + 5\hat{k}}$, $\vec{C}\brak{4\hat{i} + 2\hat{j} -2 \hat{k}}$, $\vec{D}\brak{6\hat{i} + 5\hat{j} - \hat{k}}$ are coplanar.

\item Find the vector equation of the plane determined by the points $\vec{A}\brak{3, -1, 2}, \vec{B}\brak{5, 2, 4}$ and $\vec{C}\brak{-1, -1, 6}$. Hence, find the distance of the plane, thus obtained,from the origin.

\item Find the coordinates of the foot of the perpendicular $\vec{Q}$ drawn from $\vec{P}\brak{3, 2, 1}$ to the plane $2x - y + z + 1 = 0$. Also, find the distance $\vec{P}\vec{Q}$ and the image of the point $\vec{P}$ treating this plane as a mirror.

