\item Ishan wants to donate a rectangular plot of land for a school in his village .When he was asked to give dimensions of the plot,he told that if its length is decreased by 50m and breadth is increased by 50m,then its area will remain same,but if its length is decreased by 10m and breadth is decreased by 20m,then its area will decrease by 5300 $m^{2}$. Using matrices,find the dimensions of plot.Also give reason why he wants to donate the plot for a school.
\item A diet is to contain at least 80 units of vitamin A and 100 units of minerals.Two foods F1 and F2 are available at costing \rupee~5 per unit \rupee~6 per unit respectively.One unit of food F1 contains 4 units of vitamin A and 3 units of minerals whereas one unit of food F2 contains  3 units of vitamins A and 6 units of minerals.Formulate this as a linear programming problem.Find the minimum cost of diet that consists of mixture of these two foods and also meets minimum nutritional requirement.
\item A company manufactures two types of cardigans:type A and type B.It costs \rupee~360 to make a type A cardigan and \rupee~120 to make a type B cardigan.The company can make at most \rupee~300 cardigans and spend at most \rupee~72000 a day.The number of cardigans of type B cannot exceed the number of cardigans of type A by more than \rupee~200.The company makes a profit of \rupee~100 for each cardigan of type A and \rupee~50 for every cardigan of type B. Formulate this problem as a linear programming problem to maximise the profit to the company.Solve it graphically and find maximum profit.
\item A retired person wants to invest an amount  of \rupee~50,000. His broker recommends investing in two type of bonds $'A'$ and $'B'$ yielding $10\%$ and $9\%$ return respectively on the invested amount. He decides to invest at least \rupee~20,000 in bond $'A'$ and at least \rupee~10,000 in bond $'B'$. He also wants to invest at least as much in bond $'A'$ as in bond $'B'$. Solve this linear programming problem graphically to maximise his returns.
\item Write the coordinates of the point which is the reflection of the point$({\alpha},{\beta},{\gamma}) $ in the $ XZ$ - plane.
																				      								        																																					\item On her birthday Seema decided to donate some money to children of an orphanage home. If there were 8 children less,every one would have got \rupee~10 more.However,if there were 16 children more,every one would have got \rupee~10 less.Using matrix method,find the number of children and the amount distributed by Seema.What values are reflected by Seema's decision?
\item Find the coordinates of the foot of perpendicular and perpendicular distance from the point p(4,3,2) to the plane x+2y+3z=2.Also find the image of P in the plane.
\item A typist charges \rupee~145 for typing $10$ English and $3$ Hindi pages, while charges for typing $3$ English and $10$ Hindi pages are \rupee~180. Using matrices, find the charges of typing one English and one Hindi page separately. However typist charged only \rupee~2 per page from poor student Shyam for $5$ Hindi pages. How much less was charged from this poor boy? Which values are reflected in this problem.
\item For what values of $k$, the system of linear equations\\
$x+y+z=2$\\
$2x+y-z=3$\\
$3x+2y+kz=4$\\
has a unique solution?								   
																																																									 
\end{enumerate}
	
