\begin{enumerate}
	\item A diet is to contain at least $80$ units of Vitamin $A$ and $100$ units of minerals.
	      Two foods $\text{F}_1$ and $\text{F}_2$ are available costing $5$ rupees per unit and $6$ rupees per unit respectively.
	      One unit of food $\text{F}_1$ contains $4$ units of vitamin $A$ and $3$ units of minerals whereas
	      one unit of food $\text{F}_2$ contains $3$ units of vitamin $A$ and $6$ units of minerals.
	      Formulate this as a linear programming problem. Find the minimum cost of diet that consists of mixture of these two foods and also meets minimum nutritional requirement.


	\item  A retired person wants to invest an amount of $50,000$ rupees. His broker recommends investing in two type of bonds $A$ and $B$ yielding $10\%$ and $9\%$ return respectively on the invested amount. He decides to invest at least
	      $20,000$ rupees in bond $A$ and at least $10,000$ rupees in bond $B$. He also wants to invest at least as much in bond $A$ as in bond $B$. Solve this linear programming problem graphically to maximise his returns.

	\item A typist charges $145$ rupees for typing $10$ English and $3$ Hindi pages, while charges for typing $3$ English and $10$ Hindi pages are $180$ rupees. Using matrices,
	      find the charges of typing one English and one Hindi page separately.
	      However typist charged only $2$ rupees per page from a poor student Shayam for $5$ Hindi pages.
	      How mcuh less was charged from ths poor boy? which values are reflected in this problem?
	\item There are two types of fertilisers $A$ and $B$. $A$ consists of $12$\% nitrogen and $5$\% phosphoric acid whereas $B$ consists of $4$\% nitrogen and $5$\% phosphoric acid. After testing the soil conditions, farmer finds that he needs at least $12$ kg of nitrogen and $12$ kg of phosphoric acid for his crops. If $A$ costs \rupee $10$ per kg and $B$ cost \rupee $8$ per kg, then graphically determine how much of each type of fertiliser should be used so that nutrient requirements are met at a minimum cost.
	\item A company manufactures two types of cardigans : type $A$ and type $B$. It costs \rupee $360$ to make a type $A$ cardigan and \rupee $120$ to make a type $B$ cardigan. The company can make at most $300$ cardigans and spend at most \rupee $72,000$ a day. The number of cardigans of type $B$ cannot exceed the number of cardigans of type $A$ by more than $200$. The company makes a profit of \rupee $100$ for each cardigan of type $A$ and \rupee $50$ for every cardigan of type $B$. Formulate this problem as a linear programming problem to maximise the profit to the company. Solve it graphically and find maximum profit.
	\item A typist charges \rupee $145$ for typing $10$ English and $3$ Hindi pages, while charges for typing $3$ English and $10$ Hindi pages are \rupee $180$. Using matrices, find the charges of typing one English and one English page separately. However typist charged only \rupee $2$ per page from a poor student Shyam for $5$ Hindi pages. How much less was charged from this poor boy? Which values are reflected in this problem?

	\item A retired person wants to invest an amount of \rupee $50,000$. His broker recommends investing in the type of bonds '$A$' and '$B$' yielding $10\%$ and $9\%$ return respectively on the invested amount. He decides to invest at least \rupee $20,000$ in bond '$A$' and at least \rupee $10,000$ in bond '$B$'. He also wants to invest at least as much in bond '$A$' as in bond '$B$'. Solve this linear programming problem graphically to maximise his returns.
	\item There are two types of fertilisers \lq A\rq and \lq B\rq. \lq A\rq consists of $12\%$ nitrogen and $5\%$ phosphoric acid whereas \lq B\rq consists of $4\%$ nitrogen and $5\%$ phosphoric acid. After testing the soil conditions, farmer finds that he needs at least $12$ kg of nitrogen and $12$ kg of phosphoric acid for his crops. If \lq A\rq costs \rupee $10$ per kg and \lq B\rq cost \rupee $8$ per kg, then graphically determine how much of each type of fertiliser should be used so that nutrients requirements are met at a minimum cost.
	\item A company manufactures two types of cardigans:type A and type B.It costs \rupee~360 to make a type A cardigan and \rupee~120 to make a type B cardigan.The company can make at most \rupee~300 cardigans and spend at most \rupee~72000 a day.The number of cardigans of type B cannot exceed the number of cardigans of type A by more than \rupee~200.The company makes a profit of \rupee~100 for each cardigan of type A and \rupee~50 for every cardigan of type B.
	      Formulate this problem as a linear programming problem to maximise the profit to the company.Solve it graphically and find maximum profit.	
 	\item A diet is to contain 80 units of Vitamin A and 100 units of minerals. Two foods $F_1$ and $F_2$ are available, costing \rupee 5 per unit and \rupee 6 per unit, respectively. One unit of food $F_1$ contains 4 units of vitamin A and 3 units of minerals whereas one unit of food $F_2$ contains 3 units of vitamin A and 6 units of minerals. Formulate this as a linear programming problem. Find the minimum cost of diet that consists of mixture of these two foods and also meets minimum nutritional requirement.


