\begin{enumerate}
    \item There are two bags $A$ and $B$. Bag $A$ contains $3$ white and $4$ red balls whereas bag $B$ contains $4$ white and $3$ red balls. Three balls are drawn at random (without replacement) from one of the bags and are found to be two white and one red. Find the probability that these were drawn from bag $B$.

    \item Three numbers are selected at random (without replacement) from first six positive integers. If $X$ denotes the smallest of the three numbers obtained, find the probability distribution of $X$. Also find the mean and variance of the distribution.


    \item A bag $X$ contains $4$ white balls and $2$ black balls, while another bag $Y$ contains
          $3$ white balls and $3$ black balls. Two balls are drawn (without replacement) at
          random from one of the bags and were found to be one white and one black.
          Find the probability that the balls were drawn from bag $Y$.

    \item $A$ and $B$ throw a pair of dice alternately, till one of them gets a total of 10 and
          wins the game. Find their respective probabilities of winning, if $A$ starts first.

    \item Three numbers are selected at random (without replacement) from first six
          positive integers. Let $X$ denote the largest of the three numbers obtained. Find
          the probability distribution of $X$. Also, find the mean and variance of the
          distribution.
    \item $A, B$ and $C$ throw a pair of dice in that order alternately till one of them gets a total of $9$ and wins the game. Find their respective probabilities of winning, if $A$ starts first.
    \item A random variable $X$ has the following probability distribution :
          \begin{table}[h!]
              \begin{center}
                  \begin{tabular}{|c |c| c | c | c | c | c | c |}
                      \hline
                      X        & 0   & 1    & 2    & 3    & 4     & 5      & 6         \\
                      \hline
                      $\pr{X}$ & $C$ & $2C$ & $2C$ & $3C$ & $C^2$ & $2C^2$ & $7C^2 +C$ \\
                      \hline
                  \end{tabular}
              \end{center}
          \end{table}
          Find the value of $C$ and also calculate mean of the distribution.
    \item A committee of $4$ students is selected at random from a group consisting of $7$ boys and $4$ girls. Find the probability that there are exactly $2$ boys in the committee, given that at least one girl must be there in the committee.
    \item Five bad oranges are accidently mixed with $20$ good ones. If four oranges are drawn one by one successively with replacement, then find the probability distribution of number of bad oranges drawn. Hence find the mean and variance of the distribution.
    \item In a game, a man wins \rupee $5$ for getting a number greater than $4$ and loses \rupee $1$ otherwise, when a fair die is thrown. The man decided to throw a die thrice but to quit as and when he gets a number greater than $4$. Find the expected value of the amound he wins/loses.
    \item A bag contains $4$ balls. Two balls are drawn at random \brak{\text{without replacement}} and are found to be white. What is the probability that all balls in the bag are white ?
    \item A committee of $4$ students is selected at random from a group consisting of $7$ boys and $4$ girls. Find the probability that there are exactly $2$ boys in the committee, given that at least one girl must be there in the committee.
    \item A random variable $X$ has the following probability distribution:
          \begin{center}
              \begin{tabular}{|c|c|c|c|c|c|c|c|}
                  \hline
                  $X$         & $0$ & $1$  & $2$  & $3$  & $4$   & $5$    & $6$      \\
                  \hline
                  $P\brak{X}$ & $C$ & $2C$ & $2C$ & $3C$ & $C^2$ & $2C^2$ & $7C^2+C$ \\
                  \hline
              \end{tabular}
          \end{center}
          Find the value of $C$ and also calculate mean of the distribution.
    \item $A$, $B$ and $C$ throw a pair of dice in that order alternately till one of them gets a total of $9$ and wins the game. Find their respective probabilities of winning, if $A$ starts first.

    \item A bag $X$ contains $4$ white balls and $2$ black balls, while another bag $Y$ contains $3$ white balls and $3$ black balls. Two balls are drawn (without replacement) at random from one of the bags and were found to be one white and one black. Find the probability that the balls were drawn from bag $Y$.

    \item $A$ and $B$ throw a pair of dice alternately, till one of them gets a total of $10$ and wins the game. Find their respective probabilities of winning, if $A$ starts first.

    \item Three numbers are selected at random (without replacement) from first six positive integers. Let $X$ denote the largest of the three numbers obtained. Find the probability distribution of $X$. Also, find the mean and variance of the distribution.
    \item In a game, a man wins \rupee $5$ for getting a number greater than 4 and loses \rupee $1$ otherwise, then a fair die is thrown. The man decided to throw a die thrice but  quit as and when he gets a number greater than $4$. Find the expected value of the amount he wins/loses.

    \item A bag contains $4$ balls. Two balls are drawn at random (without replacement) and are found to be white. What is the probability that all balls in the bag are white.
    \item A bag $X$ contains $4$ white balls and $2$ black balls, while another bag $Y$ contains $3$ white balls and $3$ black balls. Two balls are drawn (without replacement) at random from  one of the bags and where found to be one white and one black. Find the probability that the balls were  drawn from bag $Y$.
    \item $A$ and $B$ throw a pair of alternatively, till one of them gets a total of $10$ and wins the game. Find their respective probabilities of winning, if $A$ starts first.
    \item Three numbers are selected at random (without replacement) from first six positive integers. Let $X$ denote the largest of the three numbers obtained. Find the probability distribution of $X$. Also, find the mean and variance of the distribution.
    \item A committee of 4 students is selected at random from a group consisting of 7 boys and 4 girls.Find the probability that there are exactly 2 boys in the committee,given that at least one girl must be there in the committee.

    \item A random variable X has the following probability distribution:\\
          \begin{tabular}{|c|c|c|c|c|c|c|c|}
              \hline
              X      & 0   & 1    & 2    & 3    & 4       & 5        & 6          \\
              \hline
              $P(X)$ & $C$ & $2C$ & $2C$ & $3C$ & $C^{2}$ & $2C^{2}$ & $7C^{2}+C$ \\
              \hline
          \end{tabular}\\
          find the value of C and also calculate mean of the distribution.
    \item A,B and C throw a pair of dice in that order alternately till one of them gets a total of 9 and wins the game.Find their respective probabilities of winning if A starts first.
    \item There are two bags A and B.Bag A contains 3 white and 4 red balls whereas bag B contains 4 white and 3 red balls.Three balls are drawn at random(without replacement) from one of the bags are found to be two white and one red.Find the probability that these were drawn from bag B.
    \item There are two bags A and B. Bag A contains $3$ white and $4$ red balls whereas bag B contains $4$ white and $3$ red balls. Three balls are drawn at random (without replacement) from one of the bags and are found to be two white and one red. Find the probability that these were drawn from bag B.
    \item Three numbers are selected at random (without replacement) from first six positive integers. If $X$ denotes the smallest of the three numbers obtained, find the probability distribution of $X$. Also find the mean and variance of the distribution.

