\begin{enumerate}
    \item A card is drawn at random from a well shuffled pack of $52$ playing cards. Find the probability of getting neither a red card nor a queen.\\
    \item There are $100$ cards in a bag on which numbers from $1$ to $100$ are written. A card is taken out from the bag at random. Find the probability that the number on the selected card
          \begin{enumerate}[label=(\roman*)]
              \item is divisible by $9$ and is a perfect square
              \item is a prime number greater than $80$
          \end{enumerate}
    \item A number $x$ is selected at random from the numbers $1, 2, 3$ and $4$. Another number $y$ is selected at random from the numbers $1, 4, 9$ and $16$. Find the probability that product of $x$ and $y$ is less than $16$.\\
    \item From a pack of $52$ playing cards, Jacks, Queens and Kings of red colour are removed. From the remaining, a card is drawn at random. Find the probability that drawn card is :
          \begin{enumerate}[label=(\roman*)]
              \item a black King
              \item a card of red colour
              \item a card of black colour
          \end{enumerate}
    \item  Three different coins are tossed together. Find the probability of getting
          \begin{enumerate}[label=(\roman*)]
              \item exactly two heads
              \item at least two heads
              \item at least two tails.

          \end{enumerate}
    \item Five bad oranges are accidentally mixed with $20$ good ones. If four oranges are drawn one by one successively with replacement, then find the probability distribution of the number of bad oranges drawn. Hence find the mean and variance of the distribution.

\end{enumerate}
