\item There are two bags A and B.Bag A contains 3 white and 4 red balls whereas bag B contains 4 white and 3 red balls.Three balls are drawn at random(without replacement) from one of the bags are found to be two white and one red.Find the probability that these were drawn from bag B.
\item Three numbers are selected at random(without replacement) from first six positive integers.If X denotes the smallest of the three numbers obtained,find the probability distribution of X.Also find the mean and variance of distribution.

\item Three numbers are selected at random (without replacement) from first six positive integers. Let $X$ denote the largest of the three numbers obtained. Find the probability distribution of $X$. Also, find the mean and variance of the distribution.    \item A bag $X$ contains $4$ white balls and $2$ black balls, while another bag $Y$ contains $3$ white balls and $3$ black balls. Two balls are drawn (without replacement) at random from  one of the bags and where found to be one white and one black. Find the probability that the balls were  drawn from bag $Y$.
\item $A$ and $B$ throw a pair of alternatively, till one of them gets a total of $10$ and wins the game. Find their respective probabilities of winning, if $A$ starts first.

\item A committee of 4 students is selected at random from a group consisting of 7 boys and 4 girls.Find the probability that there are exactly 2 boys in the committee,given that at least one girl must be there in the committee.

\item A,B and C throw a pair of dice in that order alternately till one of them gets a total of 9 and wins the game.Find their respective probabilities of winning if A starts first.
 \end{enumerate}
