\begin{enumerate}
\item A solid right circular cone is cut into two parts at the middle of its height by a plane parallel to its base. The ratio of the volume of the smaller cone to the whole cone is 
\begin{enumerate}
\item $1 : 2$ 
\item $1 : 4$ 
\item $1 : 6$ 
\item $1 : 8$ 
\end{enumerate}
\item If the radius of the base of a right circular cylinder is halved, keeping the height the same, then the ratio of the volume of the cylinder thus obtained to the volume of original cylinder is : 
\begin{enumerate}
\item $1 : 2$ 
\item $1 : 4$ 
\item $2 : 1$ 
\item $4 : 1$ 
\end{enumerate}
\item The radii of a circular ends of a bucket of height $40\text{ cm}$ are $24\text{ cm}$ and $15\text{ cm}$. The slant height $\brak{\text{in cm}}$ of the bucket is 
\begin{enumerate}
\item $51$ 
\item $49$ 
\item $43$ 
\item $41$ 
\end{enumerate}

\item A solid sphere of radius $10.5 \text{ cm}$ is melted and recast into smaller solid cones, each of radius $3.5 \text{ cm}$ and height $3 \text{ cm}$. Find the number of cones so formed. $\brak{\text{Use } \pi = \frac{22}{7}}$ 

\item A hemispherical bowl of internal radius $9 \text{ cm}$ is full of water. Its contents are emptied in a cylindrical vessel of internal radius $6 \text{ cm}$. Find the height of water in the cylindrical vessel. 


\item A hemispherical tank, full of water, is emptied by a pipe at the rate of $\frac{22}{7}$ litres per sec. How much time will it take to empty half the tank if the diameter of the base of the tank is $3 \text{ m}$? 

\item A drinking glass in the shape of the frustum of a cone of height $14 \text{ cm}$. The diameters of the two circular ends are $4 \text{ cm}$ and $2 \text{ cm}$. Find the capacity of the glass.  $\brak{\text{Use } \pi = 3.14}$ 

\item  A military tent of height $8.25 \text{ m}$ is in the form of a right circular cylinder of base diameter $30 \text{ m}$ and height $5.5 \text{ m}$ surmounted by a right circular cone of same base radius. Find the length of the canvas use in making tent, if the breadth of the canvas is $1.5 \text{ m}$. 

\item The volume of a hemisphere is $2425\dfrac{1}{2}$ $\text{ cm}^3$. Find the curved surface area.  $\brak{\text{Use } \pi = 3.14}$ 

\item From a solid cylinder of height $7\text{ cm}$ and base diameter $12\text{ cm}$, a conical cavity of same height and same base diameter is hollowed out. Find the total surface area of the remaining solid. $\brak{\text{Use } \pi = \frac{22}{7}}$ 

\item A cylindrical bucket, $32 \text{ cm}$ high and with radius of base is $18 \text{ cm}$, is filled with sand. This bucket is emptied on the ground and a conical heap of sand is formed. If the height of the conical heap is $24 \text{ cm}$, then find the radius sand slant height of the heap. 


\item A solid is in the shape of a cone surmounted on a hemisphere, the radius of each of them being $3.5\text{ cm}$ and the total height of solid is $9.5\text{ cm}$. Find the volume of the solid. $\brak{\text{Use } \pi = \frac{22}{7}}$ 

\item A bucket is in the form of a frustum of a cone and it can hold $28.499$ litres of water. If the radii of its circular ends are $28\text{ cm}$ and $21\text{ cm}$, find the height of the bucket. $\brak{\text{Use } \pi = \frac{22}{7}}$ 


\item A solid is in the shape of a cone mounted on a hemisphere of same base radius. If the curved surface area of the hemispherical part and the conical part are equal, then find the ratio of the radius and the height of the conical part. 

\item A sphere of diameter $6\text{ cm}$ is dropped into a cylindrical vessel, partly filled with water, whose diameter is $12\text{ cm}$. If the sphere is completely submerged in water, by how much will the surface of water be raised in cylindrical vessel ? 
\item A toy is in the shape of a cone mounted on a hemisphere of same base radius. If the volume of the toy is $231\text{ cm}^3$ and its diameter is $7\text{ cm}$, then find the height of the toy.  $\brak{\text{Use } \pi = \frac{22}{7}}$ 

\item The radii of internal and external surfaces of a hollow spherical shell are $3\text{ cm}$ and $5\text{ cm}$ respectively. It is melted and recast into a solid cylinder of diameter $14\text{ cm}$. Find the height of the cylinder. 

\item A drinking glass is in the shape of a frustum of a cone of height $14\text{ cm}$. The diameters of its two circular ends are $16\text{ cm}$ and $12\text{ cm}$. Find the capacity of the glass. $\brak{\text{Use } \pi = \frac{22}{7}}$ 

\end{enumerate}
