\begin{enumerate}
\item Cards bearing numbers $2, 3, 4, \ldots, 11$ are kept in a bag. A card is drawn at random from the bag. The probability of getting a card with a prime number is 
\begin{enumerate}
\item $\dfrac{1}{2}$ 
\item $\dfrac{2}{5}$ 
\item $\dfrac{3}{10}$ 
\item $\dfrac{5}{9}$ 
\end{enumerate}
\item Two dices are thrown together. The probability of getting the same number on both dices is : 
\begin{enumerate}
\item $\dfrac{1}{2}$ 
\item $\dfrac{1}{3}$ 
\item $\dfrac{1}{6}$ 
\item $\dfrac{1}{12}$ 
\end{enumerate}
\item The probability of a non-leap year having $53$ Mondays is  
\begin{enumerate}
\item $\dfrac{2}{7}$ 
\item $\dfrac{1}{7}$ 
\item $\dfrac{5}{7}$ 
\item $\dfrac{6}{7}$ 
\end{enumerate}
%Probability
\item A card is drawn at random from a well shuffled pack of $52$ cards. Find the probability of getting 
\begin{enumerate}[label=\Roman*.]
\item a red king. 
\item a queen or a jack. 
\end{enumerate}
%Probability
\item All kings, queens and aces are removed from a pack of $52$ cards. The remaining cards are well shuffled and then a card is drawn from it. Find the probability that the drawn card is  
\begin{enumerate}[label=\Roman*.]
\item a black face card. 
\item a red card. 
\end{enumerate}
%probability

%probability
\item A number is selected at random from first $50$ natural numbers. Find the probability that it is a multiple of $3$ and $4$. 
%probability
\item A box contains $100$ red cards, $200$ yellow cards and $50$ blue cards. If a card is drawn at random from the box, then find the probability that it will be \begin{enumerate}[label=\Roman*.]
\item a blue card
\item not a yellow card
\item neither a yellow nor a blue card. 
\end{enumerate}

\item A child has a die whose six faces show the letters as shown in \figref{2012_p_fig1}.The die is thrown once. Find the probability of getting 
\begin{figure}[ht]
\centering
\begin{tikzpicture}[scale = 5]

  % Draw square
  \draw (0,0) rectangle (0.1,0.1);
  \draw (0.2,0) rectangle (0.3,0.1);
  \draw (0.4,0) rectangle (0.5,0.1);
  \draw (0.6,0) rectangle (0.7,0.1);
  \draw (0.8,0) rectangle (0.9,0.1);
  \draw (1,0) rectangle (1.1,0.1);
  
  % Label the center
  \node at (0.05,0.05) {A};
  \node at (0.25,0.05) {B};
  \node at (0.45,0.05) {C};
  \node at (0.65,0.05) {A};
  \node at (0.85,0.05) {D};
  \node at (1.05,0.05) {A};

\end{tikzpicture}
\caption{}
\label{2012_p_fig1}
\end{figure}
\begin{enumerate}[label=\Roman*.]
\item A 
\item D 
\end{enumerate}
\item Cards marked with numbers $1,3,5, \ldots, 101$ are placed in a bag and mixed thoroughly. A card is then drawn at random from the bag. Find the probability that the number on the drawn card is 
\begin{enumerate}[label=\Roman*.]
\item less than $19$.
\item a prime number less than $20$. 
\end{enumerate}
\end{enumerate}
