\begin{enumerate}
\item A kite is flying at a height of $30 \text{ m}$ from the ground. The length of string from the kite to the ground is $60 \text{ m}$. Assuming that there is no slack in the string, the angle of elevation of the kite at the ground is 
\begin{enumerate}
\item $45\degree$ 
\item $30\degree$ 
\item $60\degree$ 
\item $90\degree$ 
\end{enumerate}
\item From a point on the ground, which is $15\text{ m}$ away from the foot of a vertical tower, the angle of elevation of the top of the tower, is found to be $60\degree$. The height of the tower in $\brak{\text{in metres}}$ is 
\begin{enumerate}
\item $5\sqrt 3$ 
\item $15\sqrt 3$ 
\item $15$ 
\item $7.5$ 
\end{enumerate}
\item The length of shadow of a tower on the plane ground is $\sqrt 3 \text{ m}$ times the height of the tower. The angle of elevation of sun is : 
\begin{enumerate}
\item $45\degree$ 
\item $30\degree$ 
\item $60\degree$ 
\item $90\degree$ 
\end{enumerate}
%Trigonometry
\item The angles of depression of the top and bottom of a tower as seen from the top of a $60\sqrt 3 \text{ m}$ high cliff are $45\degree$ and $60\degree$ respectively. Find the height of the tower. 
%Trigonometry
\item In a flight of $2800 \text{ km}$, an aircraft was slowed down due to bad weather. Its average speed is reduced by $100 \text{ km/h}$ and time is increased by $30$ minutes. Find the original duration of flight. 
%Trigonometry
\item The angles of elevation and depression of the top and bottom of a light-house from the top of a $60 \text{ m}$ high building are $30\degree$ and $60\degree$ respectively. Find 
\begin{enumerate}[label=\Roman*.]
\item the difference between the heights of the light-house and the building. 
\item the distance between light-house and building. 
\end{enumerate}
%trigonometry
\item The angles of depression of two ships from the top of a light house and on the same side of it are found to be $45\degree$ and $30\degree$. if the ships are $200 \text{ km}$ apart, find the height of the light house. 
\item The angle of elevation of the top of a hill at the foot of a tower is $60\degree$ and the angle of depression from the top of the tower of the foot of the hill is $30\degree$. If the tower is $50\text{ m}$ high, find the height of the hill. 
\item From the top of a tower $50\text{ m}$ high, the angle of depression of the top of a pole is $45\degree$ and from the foot of the pole, the angle of elevation of the top of the tower is $60\degree$. find the height of the pole if the pole and tower stand on the same plane. 
\item The angle of depression from the top of a tower of a point $A$ on the ground is $30\degree$. On moving a distance of $20\text{ m}$ from the point $A$ towards the foot of the tower to a point $B$ the angle of elevation of the top of the tower from point $B$ is $60\degree$. Find the height of the tower and its distance from point $A$.
\end{enumerate}
