\item The perimeter $\brak{in\,cm}$ of a square circumscribing a circle of radius $a$ cm, is  
\begin{enumerate}[label=(\Alph*)]
    \item $8a$
    \item $4a$
    \item $2a$
    \item $16a$
\end{enumerate}
\item The radius $\brak{in\,cm}$ of the largest right circular cone that can be cut out from a cube of edge $4.2$ cm is

\begin{enumerate}[label=(\Alph*)]
\item $4.2$
\item $2.1$
\item $8.4$
\item $1.05$
\end{enumerate}

\item An open metal bucket is in the shape of a frustum of a cone of height $21$ cm with radii of its lower and upper ends as $10$ cm and $20$ cm at Rs. $30$ per liter. Find the cost of milk which can completely fill the bucket at Rs $30$ per liter. 

[Use $\pi = \dfrac{22}{7}$]

\item Find the area of the triangle formed by joining the mid-points of the sides of the triangle whose vertices are $A(2, 1)$, $B(4, 3)$, and $C(2, 5)$.


\item Two cubes each of volume 27 ${cm}^3$ are joined end to end to form a solid. Find the surface area of the resulting cuboid.

\item A cone of height $20$ cm and radius of base $5$ cm is made up of modelling clay. A child reshapes it in the form of a sphere. Find the diameter of the sphere.

\item Water is flowing at the rate of $15$ km/hour through a pipe of diameter $14$ cm into a cuboidal pond which is $50$ m long and $44$ m wide. In what time will the level of water in the pond rise by $21$ cm?


\item A train travels $180$ km at a uniform speed. If the speed had been $9$ km/hour more, it would have taken $1$ hour less for the same journey. Find the speed of the train.
\end{enumerate}
