\begin{enumerate}
\item If the corner points $(3, 4)$ and $(5, 0)$ of the fesible region in an $LPP$, give the same maximum value for the objective function $z = ax + by$, where $a, b > 0$, then we have
\begin{enumerate}
\item $a = 2b$
\item $2a = b$
\item $2a = 3b$
\item $3b = 2a$
\end{enumerate}

\item A dietician wishes to mix two types of foods in such a way that vitamin contents of the mixture contain at least 8 units of vitamin A and 10 units of vitamin C. Food I contains 2 units/kg of vitamin A and 1 unit/kg of vitamin C. Food II contains 1 unit/kg of vitamin A and 2 units/kg of vitamin C. It costs \rupee 50 per kg to purchase Food I and \rupee 70 per kg to purchase Food II. Formulate this probblem as a Linear Programming Problem for minimising the cost of such a mixture.

\item A company produces two types of goods, A and B, that require gold and silver. Each unit of type A requires 3 g of silver and 1 g of gold, while that of type B requires 1 g of silver and 2 g of gold. The company can use at the most 9 g of silver and 8 g of gold. If each unit of type A brings a profit of \rupee 120 and that of type B \rupee 150, then find the number of units of each type that the company should produce to maximise profit. 
Formulate the above LPP and solve it graphically. Also, find the maximum profit.

\item Maximize $z = 3x + 4y$, if possible,
	subject to the constraints:
		\begin{align}
			x - y \leq -1 \\
			-x + y \leq 0 \\
			x, y \geq 0
		\end{align}

\item A dietician wishes to mix two types of foods $F_1$ and $F_2$ in such a way that tha vitamin content of the mixture containsat least 8 units of vitamin A and 10 units of vitamin C.Food $F_1$ contains 2 units/kg of vitamin A and 1 unit/kg of vitamin C, while Food $F_2$ contains 1 unit/kg of vitamin A and 2 units/kg of vitamin C. It costs \rupee 5 per kg to purchase Food $F_1$ and \rupee 7 per kg to purchase Food $F_2$.\\
Based on the above information, answer the following questions:
\begin{enumerate}
	\item To find out the minimum cost of such a mixture, formulate the above problem as a LPP.
	\item Determine the minimum cost of the mixture.
\end{enumerate}

\end{enumerate}
