\documentclass[20pt,-letter paper]{article}
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{mathtools}
\providecommand{\myvec}[1]{\ensuremath{\left\{#1\right\}}}

\title{Algebra assignment}
%\author{Prof.G V V sharma}
\date{\today}
\begin{document}
\maketitle{Questions}


\begin{enumerate}

\item If one zero of the polynomial $p(x) = (a^2+4)X^2+20X+4a$ is reciprocal of the other, find the value of $a$.

\item Find the roots of the quadratic equation
\begin{align}
 X^2+X-(a+1)(a+2)=0
\end{align}

\item  Solve for x :
\begin{align}
 10X-\frac{1}{X} = 3, X \ne {0}
\end{align}
\item In $\triangle ABC $ , $\angle B = 90\degree$ and $ \tan A = \frac{1}{\sqrt{3}}$.Then find the value of $\sin A \cos C + \cos A\sin C $



\item If $ X = a\sin\theta +b\cos\theta$ and $ y = a\cos\theta - b\sin\theta$,then find the value of $(X^2+Y^2)$.

\item Answer any \textbf{four} of the following questions:
\begin{enumerate}  
\item The sum and the product of the zeroes of a quadratic polynomial are -1 and -12 respectively. The polynomial is 
\begin{enumerate}  
\item $X^2-X-12$
\item $X^2+X-12$
\item $X^2-X+12$
\item $X^2+X+12$
\end{enumerate}  
\item The zeroes of the quadratic polynomial $x^2+20x+91$ are
\begin{enumerate}  
\item both positive.
\item both equal.
\item both negative.
\item one positive and one negative.  
\end{enumerate}  
\item  If the zeroes of the polynomial $5x^2-26x+k$ are reciprocal of each other, then the value of k is 
\begin{enumerate}  
\item  $5$
\item -$5$
\item  $\frac{1}{5}$
\item -$\frac{1}{5}$
\end{enumerate}  
\item   If $\alpha,\beta$ are the zeroes of the polynomial $x^2-5x-14$, then the value of $\alpha\beta-\alpha-\beta$ is
\begin{enumerate}  
\item -$9$
\item  $19$
\item  $9$
\item -$19$
\end{enumerate}  
\item What should be added to the polynomial $x^2-5x+4$, so that $3$ is a zero of the resulting polynomial ? 
\begin{enumerate}  
\item $5$
\item $4$
\item $2$
\item $1$
\end{enumerate} 
\end{enumerate}

\item If $2\sin 2A=\sqrt{3}$ , then find the value of A.

\item If $7\sin^2\theta + 3\cos^2\theta = 4$, then show that $\tan\theta= \frac{1}{\sqrt{3}}$, $0\degree <\theta < 90\degree$

\item Find the quadratic polynomial whose zeroes are $(\sqrt{5}-4) \text{and}(\sqrt{5}+4)$.

\item If the sum of $LCM$ and $HCF$ of two numbers is $1260$ and the $LCM$ is $900$ more than their $HCF$, find their $LCM$.

\item Find the values of m and n for which x=2 and x=3 are the roots of the quadratic equation $3x^2-2mx+2n=0$.

 \item Divide $19$ into two parts such that sum of their squares is $193$.

\item The angles of depression of the top and bottom of an $8$ m tall building from the top of a multi-storeyed building are $30\degree$ \text{and} $45\degree$ respectively. Find the height of the multi-storeyed building.

\item From a point on the ground, the angles of elevation of the bottom and top of a transmission tower fixed on the top of a $20$m high building are $45\degree$ \text{and} $60\degree$ respectively. Find the height of the tower.

 \item As observed from the top of $75$m high lighthouse from the sea-level,the angles of depression of two ships are $30\degree$ \text{and}  $45\degree$. If one ship is exactly behind the other on the same side of the lighthouse, find the distance between the two ships.

\item It takes $12$ hours to fill a swimming pool using two pipes together. If the larger pipe is used for $4$ hours and smaller pipe is used for $9$ hours, only half of the pool is filled. How long will it take for each pipe alone to fill the  pool? 

\end{enumerate}
\end{document}
