\documentclass[20pt,-letter paper]{article}
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{mathtools}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\title{}
%\author{Prof.G V V sharma}
\date{\today}

\begin{document}

\maketitle{Questions}

\begin{enumerate}
\item Find the sum and product of zeroes of the polynomial $p(x)=x^2+5x+6$
\item If $2\cos  \theta = \sqrt{3}$ , then find the value of $\theta$
\item Find the discriminant of the quadratic equation $2x^2-5x-6=0$.
\item  In $\triangle ABC$, right-angled at $A$, if $AB=7 cm$ and $AC=24 cm$, then find $\sin B$
and $\tan C$.

\item \begin{enumerate}

\item If  $\sin (A+B) = \sqrt{3}/2,
 \sin (A-B) = 1/2,$ Where $0\degree<A+B<90\degree; A>B$, then find the values of $A$ and $B$.

\item  Simplify :
\begin{align}
\frac{\sin 30\degree + \tan 45\degree-\cos 60\degree}{\sec 30\degree + \cos 60\degree + \cot 45\degree} 
\end{align}
\end{enumerate}


\item The greater of two supplementary angles exceeds the smaller by $18\degree$. Find the two angles.

\item  Prove that $7 \sqrt{2}$ is an irrational number ,given that $\sqrt{2}$ is an irrational number.

\item \begin{enumerate}
\item Prove that :
\begin{align}
 \sec \theta (1-\sin\theta)(\sec\theta+ \tan\theta)=1
\end{align}

\item Prove that :
\begin{align}
\frac{1+\sec A}{\sec A}=\frac{\sin^2 A}{1-\cos A} 
\end{align}
\end{enumerate}

\item If $\alpha,\beta$ are the zeroes of the quadratic polynomial $x^2+9x+20$, from a quadratic polynomial whose zeroes are  $(\alpha+1)$ and 
$(\beta+1)$.


\item \begin{enumerate}
\item The diagonal of a rectangular field is $60$ meters more than the shorter side, find the sides of the field.


\item The sum of the ages of a father and his son is $45$ years. Five years ago, the product of their ages (in years) was $124 $. Determine their present ages

\end{enumerate} 


\item Write a quadratic polynomial sum of Whose zeroes is $-5
$ and product is $6$.



\item If the sum of the zeroes of the polynomial $2x^2-3ax+4$ is $6$, then the value of a 
\begin{enumerate}
\item $4$
\item $-4$
\item $2$
\item $-2$
\end{enumerate}

\item The common zero of the polynomials $x^3+1, x^2-1$ and $x^2+2x+1$ is 
\begin{enumerate}
\item $-2$
\item $-1$
\item  $1$
\item  $2$
\end{enumerate}

\item If $\alpha,\beta$ are the zeroes of the polynomial $x^2 - 4x+6$, then the value of $\alpha\beta$ is
\begin{enumerate}
\item $4$
\item $-4$
\item $6$
\item $-6$
\end{enumerate}

\item The zeroes of the polynomial $3x^2-5x-2$ are 
\begin{enumerate}
\item $\frac{1}{3}$,$2$
\item $-\frac{1}{3}$,$2$
\item $\frac{1}{3}$,-$2$
\item $-\frac{1}{3}$,-$2$
\end{enumerate}

\item If is a zero of the polynomial $p(x)=ax^2-3(a-1)x-1$  then the value of a is 
\begin{enumerate}
\item $\frac{1}{3}$,$2$
\item $-\frac{1}{3}$,$2$
\item $\frac{1}{3}$,-$2$
\item $-\frac{1}{3}$,-$2$
\end{enumerate}



\item If  $\tan \theta = 4/3$, find the value 
$\frac{2\sin \theta -3\cos \theta}{2\sin\theta+3\cos\theta}$

\item If x=  $a\cos\theta$ and y=$b\sin\theta$, then find the value of   $b^2x^2+a^2y^2$

\item A number consists of two digits whose sum is $9$. if $27$ is added to the number, the digits are reversed. Find the number
\item Prove that :
\begin{align}
\frac{\tan\theta-\cot\theta}{\sin\theta\cos\theta}=\tan^2\theta-\cot^2\theta 
\end{align}
\item Prove that:
\begin{align}
(\sec\theta-\tan\theta)^2 =\frac{1+\sin\theta}{1-\sin\theta}
\end{align}

\item The sum of the squares of three consecutive positive 
integers is $110$. Find the positive integers.

\item Ram can row a boat at the rate of $4$ km/hour in still 
water. If he takes $8$ hours in going $12$ km upstream and 
$12$ km downstream, find the speed of the stream.
\end{enumerate}
\end{document}
